The pollination trade-off

### 2019-03-05 paper/manuscript.Rmd
some changes to second subsection of the results

## Effect of ecological strategies in the pollination service

@@

We then examined the role that four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play on pollen deposition and, by extension, in the quantity and quality of pollination. 
These variables define the strategies that plants use to minimise competition for pollination. 
We found that the linear mixed models of pollen deposition used had high explanatory power. 
The conditional coefficient of determination R^2^~(c)~ of the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean of `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of the conspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen [@nakagawa_general_2013]. 
A large portion of this explanatory power came from the random effects, particularly for models of conspecific pollen. 
The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained for the fixed variables alone, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.

We tested two structures for the random effects. 
As determined by the AICc, the random structure best supported by the data was the one that fits an intercept for each species in a community independently (as opposed to an intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).

>>>>

## Ecological constraints in the pollination service

@@

We then examined the potential roles played by four ecological variables (number of shared pollinators, abundance, mean visit effectiveness, and functional originality) play in pollen deposition and, by extension, in the quantity and quality of pollination. 
Together these variables can describe the niche that plants might occupy in the context of competition for pollination. 
We found that our linear mixed models of pollen deposition had high explanatory power. 
The conditional coefficient of determination R^2^~(c)~ of the most parsimonious models (those with the lowest AICc) ranged between `r r2_values$r2c_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "conspecific_abs"]` (mean of `r r2_values$r2c_mean[r2_values$pollen_category == "conspecific_abs"]`) for the bootstrap replicates of the conspecific pollen models and between `r r2_values$r2c_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2c_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2c_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the models of heterospecific pollen [@nakagawa_general_2013]. 
A large portion of this explanatory power came from the random effects, particularly for models of conspecific pollen. 
The marginal coefficient of determination R^2^~(m)~, which describes the proportion of variance explained by just the fixed effects, ranged between `r r2_values$r2m_min[r2_values$pollen_category == "conspecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "conspecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "conspecific_abs"]`) for the conspecific models and between `r r2_values$r2m_min[r2_values$pollen_category == "heterospecific_abs"]` and `r r2_values$r2m_max[r2_values$pollen_category == "heterospecific_abs"]` (mean `r r2_values$r2m_mean[r2_values$pollen_category == "heterospecific_abs"]`) for the heterospecific models.

We tested two structures for the random effects. 
As determined by AICc, the random structure best supported by the data was the one that fit an intercept for each species in each community (as opposed to a common intercept for each species irrespective of the community they belong to). 
This structure was best for both the models of conspecific and heterospecific pollen (Table SXX).
